Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparison\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-20 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
revised Section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. 
Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes.
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EG2} and \textit{EG3}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EG2}). Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling. The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value. However, there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because of the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our formal synthesis approach. To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method.

Concerning to charge controllers, as it was reported in this section, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro.

Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparison.

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this will validate the results obtained, and it allows a simulation-verification comparison.

>>>>

CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): CPAchecker produced the results within the time limit, which varied from $2.24$ to $3.92$ hours. Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. The violation (SAT result) indicated in Table~\ref{tab1} is the $assert$ of Line $22$ at Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; these results partially answer the \textit{EG2} and \textit{EG3} \textcolor{red}{why? explain it here...}.

HOMER Pro was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$) within a time shorter than $30$ seconds, which was faster than the proposed automated synthesis tool (cf.~\textit{EG3}) \textcolor{red}{why do we need to publish our results then?}. HOME Pro was unable to simulate case study $3$ since it does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year \textcolor{red}{Does this feature add more complexity to our synthesis model? If so, we have to point it out here}.

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, we have observed that most results are quite similar in terms of technical solution and cost (cf. Table~\ref{tab1}) \textcolor{red}{If the results are quite similar and HOME Pro is faster, what is the purpose of our method here?}. Mainly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into our synthesis model, thus making it more precise. \textcolor{red}{this sentence is unclear... Our premise to adopt a fixed annual cost for operation and maintenance is that it can produce some impact at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value}. We have observed that there exists a vast divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than our synthesis tool, probably because of the operation and maintenance costs assumed by our approach were underestimated to that specific load \textcolor{red}{is it good or bad? the way you have written looks like HOME Pro is the best option}.

In general, the size of the PV panels and battery bank were larger in HOMER Pro than with our synthesis approach. To compare the results obtained from the optimization, the authors have four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State, Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, with a configuration of $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These deployed systems are closer to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EG1}.

For the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore, this feature is a PRO to the formal synthesis method. Concerning the charge controllers, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOMER Pro. Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparison.

@@

We have reported a favorable assessment of the proposed method. Nevertheless, we have also identified four threats to the validity of our results that can be further assessed and constitute future work: (1) improvement of the power reliability analysis: to include loss of load probability or loss of power supply probability, which can make the analysis more accurate; (2) improvement of the system cost analysis by including operational and maintenance costs to the adopted LCC analysis; (3) to increase the equipment and manufacturers database: this will increase the complexity of the optimization, but the result will also allow improved sizing; and (4) to compare the results of our approach with an off-the-shelf PV sizing/optimization software: this comparison will validate the results obtained, and it allows a simulation-verification comparison.
